Dynamical Stochastic Approximation Monte Carlo

### 2018-04-25 papers/histogram/sad.tex
changed to plot average entropy error in sad.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with
  SAD serving as the `golden'
  standard.}\label{fig:N50-ff0.3-max-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_10-N50-max-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with SAD serving as
  the `golden' standard.}\label{fig:N50-ff0.1-max-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_20-N50-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}\label{fig:N50-ff0.2-max-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-max-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N50-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with
  SAD serving as the `golden'
  standard.}\label{fig:N50-ff0.3-max-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_10-N50-entropy-error.pdf}
  \caption{The average entropy error for each method is shown with SAD serving as
  the `golden' standard.}\label{fig:N50-ff0.1-max-error}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_20-N50-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}\label{fig:N50-ff0.2-max-error}
\end{figure}
\begin{figure}
\includegraphics[width=\columnwidth]{figs/s000/periodic-ww1_30-ff0_30-N500-entropy-error.pdf}
  \caption{The average entropy error is shown with TMI acting as the
  `golden' standard.}
\end{figure}
